\sysfull

### 2018-04-16 paper/newCoalescing.tex

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: 
\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{coalesc\_task\_maker}(B) = B + x$; 
\end{itemize}
Since this algorithm relies on an \emph{energy blind counting process} that enlarges the coalesced task size by $x$ static tasks on a successful completion, and reduces its size by $x$ on a reboot. this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress, (see figure~\ref{fig:energyBlind}). In other words, if a coalesced task size is enlarged ten times, due to ample amount of energy or coalescing small static tasks, and then the algorithm can only progress by a single static task, due to a change in energy condition, the devise has to reboot for ten times to have an adequate coalesced task size. Moreover, This algorithm tend to experience a large re-execution penalty due to its unawareness of the energy conditions and it optimistic behavior.

\subsubsection{Energy-aware Coalescing (EA)}
\label{subsec:ECoalescing}
The Energy-aware coalescing algorithm overcomes the limitations of the previous algorithm, with out losing generality or requiring hardware support, by using the recent execution history as a metric---pure software technique---to estimate the available energy and to set the size of the coalescing task accordingly. Moreover, it takes advantage of the guarantees that the energy buffer offers on a fresh start by coalescing many static tasks. Then it approaches the expected power failure carefully by reduces the task target size by x\%, amongst 25\%, 50\% and 75\% the 50\% shows the best performance and therefore it is the default of \sys. if twice the number of the estimated tasks has been executed in the same power discharging cycle the algorithm concludes a wrong power failure time estimation has happened and enforce target re-tuning based on its new history. The EA algorithm is characterized by the following functions:

@@

>>>>

The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy, having the target budget $B$ to increase by $x$ static tasks after a successful completion of a coalesced task, and to decrease by the same number of tasks upon a reboot. In this case: 
\begin{itemize}
\item $f_\text{reboot}(B) = B - x $;
\item $f_\text{weight}(T_\text{i}) =  1$; 
\item $f_\text{coalesc\_task\_maker}(B) = B + x$; 
\end{itemize}
Since this algorithm relies on an \emph{energy blind counting process} that enlarges the coalesced task size by $x$ static tasks on a successful completion, and reduces its size by $x$ on a reboot. this algorithm is slow in reacting to the changes in energy conditions; the energy required by a coalesced task or the available energy. In particular, this algorithm can experience a large number of \emph{repeated power} failures without forward progress, (see figure~\ref{fig:energyBlind}). In other words, if a coalesced task size is enlarged ten times, due to ample amount of energy or coalescing small static tasks, and then the algorithm can only progress by a single static task, due to a change in energy condition, the device has to reboot for ten times to have an adequate coalesced task size. Moreover, This algorithm tends to experience a large re-execution penalty due to its unawareness of the energy conditions and it optimistic behavior.

\subsubsection{Energy-aware Coalescing (EA)}
\label{subsec:energyAware}
The Energy-aware coalescing algorithm overcomes the limitations of the previous algorithm, with out losing generality or requiring hardware support, by using the recent execution history as a metric---pure software technique---to estimate the available energy and to set the size of the coalescing task accordingly. Moreover, it takes advantage of the guarantees that the energy buffer offers on a fresh start by coalescing many static tasks. Then it approaches the expected power failure carefully by reduces the task target size by x\%, amongst 25\%, 50\% and 75\% the 50\% shows the best performance and therefore it is the default of \sys. if twice the number of the estimated tasks has been executed in the same power discharging cycle the algorithm concludes a wrong power failure time estimation has happened and enforce target re-tuning based on its new history. The EA algorithm is characterized by the following functions:

@@

\subsubsection{Energy- and Task-aware Coalescing (EA)}
\label{subsec:energyTaskAware}
